|

### 2020-11-30 01-Chp1-Introduction.Rmd
End of day - ahead!
Closes #1

@@

### Objective

@@

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between  
* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref():__ This Chapter seeks

@@

>>>>

```{r load_helper_scripts, include=FALSE}
source("R/citations.R")
```

@@

### Objectives

   * To review the published literature with respect to the effec tof lipids and lipid regulating agents  
   * To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
   * To meta-analyze the

@@

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid 
* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref():__ This Chapter seeks

@@

A lot of packages were used in this project`r gen_rmd_citation()`

### 2020-11-30 02-Chp2-Background.Rmd
End of day - ahead!
Closes #1

@@

@@

### History

> Two major clinical trials are often cited as providing
evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER)5
and the Medical Research
Council/British Heart Foundation Heart Protection Study27
; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate. Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript. In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences. In the MRC/BHF HPS trial,27
similar percentages ofparticipants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period. The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
*Taken from Cramer 2008 - included in review*

@@

>>>>

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```
(ref:dara-quote) --- Dara O'Briain

@@

A further clinical subtype that is of particular import the

@@

### History
> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research
Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate. Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript. In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences. In the MRC/BHF HPS trial,27
similar percentages of participants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period. The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
*Taken from Cramer 2008 - included in review*

There exist only two large scale randomized controlled trials - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b]. Both showed no effect of

Queries around how the data were collected, along

@@

## Methods used in the thesis

## Evidence synthesis

### Triangulation

### Individual patient data meta-analyis

### 2020-11-30 03-Chp2-Systematic-Review.Rmd
End of day - ahead!
Closes #1

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
Hold
```
(ref:darwin-quote) --- Charles Darwin [@chang2012]

@@

@@

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer’s Association International Conference, published in the journal Alzheimer’s & Dementia) will be searched. Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search BioArxiv, a preprint repository, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

Harmonisation of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.

@@

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:kappa-table).

>>>>

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```
(ref:dara-quote) --- Dara O'Briain

@@

Based on the review of prev, no previous

Literature con

@@

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer’s Association International Conference, published in the journal Alzheimer’s & Dementia) will be searched. Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.

@@

Following screening, XXX studies were included.

The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.

Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]

*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on XXXX and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

### 2020-11-30 04-Ch3-CPRD-Analysis.Rmd
End of day - ahead!
Closes #1

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

>>>>

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

### 2020-11-30 05-Chp-Systematic-Review-Tools.Rmd
End of day - ahead!
Closes #1

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

The `medrxivr` R package was created in order to facilitate the searching of this data source, allow

@@

```{r, eval = FALSE}
# Currently doesn't work as not on CRAN

install.packages("medrxivr")
```

@@

```{r, eval = FALSE}
devtools::install_github("mcguinlu/medrxivr")
```

@@

@@

The tool has be well received by the community, and several use cases have been reported. The tool was primarily created to faciliate the searching performed as part of the review in Chapter \@ref(sys-rev-heading). However, several other use cases have emerged for the tool. It has been used to visalise the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], etc, etc

@@

The tool has also

@@

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

This source of information is particularly important to this thesis, in that one of the primary types of evidence that I planned to use in the triangulation exercise (Mendelian randomization (MR)) is still developing and many MR studies that look at the clinical question that this project aims to investigate are posted as preprints on the bioRxiv, and more recently medRxiv, preprint servers. Being able to systematically search these records for the purpose of the systematic review described in Chapter \@(ref:sys-rev-heading) was a necessity. In light of the above, the `medrxivr` R package was created in order to facilitate the searching of this data source.

Early versions of the tool

@@

```{r, eval = FALSE}
install.packages("medrxivr")
```

@@

```{r, eval = FALSE}
devtools::install_github("ropensci/medrxivr")
```

@@

## Export

One of the key

## Data visualisation and reporter functions

**TBC**

@@

The tool has be well received by the community, and several use cases have been reported. However, several other use cases have emerged for the tool. It has been used to visalise the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], etc, etc

@@

A short paper describing the tool has been published in the Journal of Open Source Software following formal peer-review of the package and associated documentation and tutorials as part of the rOpenSci onboarding process. The entire review discussion can be viewed online.^[https://github.com/ropensci/software-review/issues/380]

The tool has been used reasonably widely, included in the systematic reviews, but also to extract data to facilitate the compare the behavior of researchers under two different journal policies by comparing the preprint paper with the published journal paper.

Feedback from the systematic review community has been positive.

### Package infrastructure

The `medrxvir` package was written in R using RStudio, and followed development best practices, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced reviewers.

The medRxiv snapshot is taken every morning using GitHub Actions, an automated system fo repetitive tasks.

## Shiny app

Part of the key theme of accessibility meant creating a web-application that l

@@

As

### 2020-11-30 97-Discussion.Rmd
Clean-up for today - ahead!
End of day - ahead!
Closes #1

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

## Summary of findings

@@

@@

Reproducible science has been a key theme running through this thesis. An open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.

>>>>

---
output:
  bookdown::word_document2: 
      reference_docx: templates/word-styles-reference-01.docx   
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```
(ref:dara-quote) --- Dara O'Briain

@@

## Summary of findings (and implications for policy makers)

@@

There are several strengths and limitations to the work presented in this thesis. One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide

@@

Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata. In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.

Containerisation was used to ensure that the code is reproducible, in line iwht best practices

Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the)

One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset. IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis). However, access is dependency on an ISAC application to the managing body of the CPRD.

### 2020-11-30 index.Rmd
End of day - ahead!
Closes #1

#######################
## bibliography path ##
#######################
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
bibliography-heading-in-pdf: Bibliography

@@

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
```
<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->

>>>>

#######################
## bibliography path ##
#######################
bibliography: 
  - bibliography/references.bib
  - bibliography/pkg-refs.bib
csl: bibliography/nature.csl
bibliography-heading-in-pdf: Bibliography

@@

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/citations.R")
```

<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->
